% vim: set filetype=latex
\documentclass[fontsize=11pt]{scrartcl}
\usepackage{amssymb,amsmath}
\usepackage[english]{babel}
\usepackage[]{moresize}

\usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}

\usepackage{tikz}
\usetikzlibrary{fadings,patterns}
\definecolor{VeryDarkGray}{gray}{0.25}
\pagestyle{empty}

% setup header fade
\newcommand\placeheader{
  \begin{tikzpicture}[remember picture,overlay]
    \node[yshift=-4cm] at (current page.north west){
      \begin{tikzpicture}[remember picture, overlay]
        \shade[top color=VeryDarkGray, bottom color=white] (0,0) rectangle (\paperwidth,4cm);
      \end{tikzpicture}
    };
  \end{tikzpicture}
}


\usepackage[mathletters]{ucs}
\usepackage[utf8x]{inputenc}
\def\@pdfborder{0 0 1}% Overrides border definition set with colorlinks=true
\def\@pdfborderstyle{/S/U/W 1}% Overrides border style set with colorlinks=true
\usepackage[]{hyperref}
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = blue, %Colour of internal links
  citecolor   = red %Colour of citations
  breaklinks=true,
  unicode=true,
  pdfborderstyle={/S/U/W 1},
}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setcounter{secnumdepth}{0}

\title{Derek C Carter}

\author{\href{mailto:dcarter@friocorte.com}{dcarter@friocorte.com}}

\begin{document}
  \placeheader
  % header stuff
  \begin{minipage}[t]{0.70\linewidth}
    \begin{flushleft}
      \subsection{Summary:}\label{summary}
      Linux administrator and trainer with fourteen years of experience.
      Building and maintaining robust, agile and scalable Linux infrastructure
      With a focus on Linux customization, core technology infrastructure,
      automation, and training.
    \end{flushleft}
  \end{minipage}
  \begin{minipage}[t]{0.30\linewidth}
    \begin{flushright}
      {\LARGE\bfseries\sffamily
        Derek C Carter\\
        \small\scshape
        Sr Linux Administrator\\
      }
      {\footnotesize\ttfamily
        \href{mailto:dcarter@friocorte.com}{dcarter@friocorte.com}\\ 
        1665 Eisenhower Ave\\Watkinsville, GA 30677\\ 
        1-(762)233-4009\\ 
        \url{http://goozbach.com/contact/}\\ 
      }
    \end{flushright}
  \end{minipage}

  \subsection{Experience}\label{experience}

  \subsubsection{\href{http://goozbach.com/}{Goozbach Infrastructure
      Solutions}}\label{goozbach-infrastructure-solutions}

  \paragraph{Linux Infrastructure Consultant and Instructor -- December
    2011 --
    Present}\label{linux-infrastructure-consultant-and-instructor-december-2011-present}

  Successful Linux Consulting and training company providing support and
  best practices for companies in the telecommunications, training and
  technology fields.

  Services provided include system updates, configuration management,
  installation automation, Bash and Python scripting, training delivery,
  training course development, and other systems administration tasks.

  \begin{itemize}
    \item
      Consulting customers on DevOps policies, procedures, and tools, using
      continuous integration (Jenkins), unit testing (Test Anything
      Protocol, Rspec), configuration management (Puppet, Ansible, CFengine,
      Salt), and installation automation (Cobbler, PXE, Kickstart)
    \item
      Creating and maintaining virtualization and ``private clouds'',
      utilizing OpenStack, SolusVM, OpenShift, Vmware, and VirtualBox
    \item
      Automating and scripting system administration tasks using Bash,
      Python, cron and at.

      \begin{itemize}
        \itemsep1pt\parskip0pt\parsep0pt
        \item
          Writing \href{https://github.com/goozbach/log4bats}{Bash libraries}
          for ease of \href{https://github.com/goozbach/bash-app}{systems
            scripting}.
      \end{itemize}
    \item
      Developing Linux systems administration training courses for The Linux
      Foundation using LaTeX, ConTeX and Docbook.

      \begin{itemize}
        \item
          Course topics include
          \href{http://training.linuxfoundation.org/linux-courses/system-administration-training/linux-enterprise-automation}{Linux
            Automation}, and
          \href{http://training.linuxfoundation.org/linux-courses/system-administration-training/linux-network-management}{Linux
            Network Management}.
        \item
          Course creation includes slides, books, lab exercises, and virtual
          server environments.
      \end{itemize}
    \item
      Delivered Linux systems administration training courses and proctored
      exams for RedHat training partners.
  \end{itemize}

  \subsubsection{\href{http://www.coraid.com/}{Coraid}}\label{coraid}

  \paragraph{QA Engineer and Tools Developer -- February 2010 -- March
    2012}\label{qa-engineer-and-tools-developer-february-2010-march-2012}

  Quality assurance engineering, testing, and tool/platform development,
  with some focus in product market fit for an Ethernet SAN Storage
  company.

  \begin{itemize}
    \item
      Testing releases of Coraid HBA drivers for Solaris, OpenIndiana,
      Nexenta, Windows, and Linux platforms; integrating Coraid storage with
      ZFS on Solaris based systems and Linux LVM.
    \item
      Testing firmware updates for Coraid appliances.
    \item
      QA tool and platform engineering

      \begin{itemize}
        \item
          Building an installation automation system using Cobbler to make
          installing and testing easier and faster.
        \item
          Integrating Cobbler into a
          \href{http://blog.friocorte.com/2011/05/chain-loading-pxe-servers.html}{Plan9
            based PXE and DHCP environment}.
        \item
          Designing and implementing automated QA testing script frameworks
          built in Bash and Python.
        \item
          Designing and installing a new testing data center.
      \end{itemize}
  \end{itemize}

  \subsubsection{\href{http://cmgdigital.com/}{Cox Media Group
      Digital}}\label{cox-media-group-digital}

  \paragraph{Sr Systems Administrator -- August 2007 -- February
    2010}\label{sr-systems-administrator-august-2007-february-2010}

  Managing day to day operations, capacity planning, operations budgeting
  and operations team lead for a leading media and publishing company with
  digital presence for Radio, TV, Newspaper, and direct marketing.

  \begin{itemize}
    \item
      Managing business merger.

      \begin{itemize}
        \item
          Migrating diverse code bases from SVN, BZR, CVS and others to Git.
        \item
          Building collaboration tools (IRC server, mailing lists, Request
          Tracker).
        \item
          Designing new server platform for new business entity.
      \end{itemize}
    \item
      Managing 100+ Linux servers serving 150+ high-traffic websites.

      \begin{itemize}
        \item
          Built automation and configuration management systems using Cobbler
          and Puppet.
        \item
          Migrating ops and dev teams from CVS to SVN.
        \item
          Building and improving deployment utilities cutting down on
          deployment time.
        \item
          Building proper DEV/QA/Staging/Production environments using KVM,
          Vmware, and Xen virtualization.
        \item
          Building and improving continuous integration testing and monitoring
          systems.
        \item
          Managing public DNS infrastructure for 200+ domains.
      \end{itemize}
    \item
      Building a new hardware architecture for a new version of our
      platform.

      \begin{itemize}
        \itemsep1pt\parskip0pt\parsep0pt
        \item
          N+1 redundant MySQL cluster, F5 LTM Load Balancers, Mod\_Perl and
          Apache, and NetAPP Storage.
      \end{itemize}
  \end{itemize}

  \subsubsection{\href{http://www.doh.state.fl.us/}{Florida Department of
      Health}}\label{florida-department-of-health}

  \paragraph{Systems Administrator -- March 2006 -- June
    2007}\label{systems-administrator-march-2006-june-2007}

  Full time Linux and VOIP consultant at agency responsible for technology
  procurement throughout the state.

  \begin{itemize}
    \item
      Designing and deploying medium scale Virtual IT help desk using
      Asterisk, with monitoring wallboard built with Jquery and Perl
    \item
      Building and maintaining state-wide, multi-agency, contact directory
      using Red Hat Directory Server, importing data from all of the
      different state agencies using custom Perl scripts.
    \item
      Building Linux based print servers using Samba, which integrated with
      Active Directory system.
  \end{itemize}

  \subsection{Additional Information}\label{additional-information}

  \paragraph{Certifications}\label{certifications}

  Red Hat Certified Engineer (RHCE) Cert
  \#\href{https://www.redhat.com/wapps/training/certification/verify.html?certNumber=110-015-385\&verify=Verify}{110-015-385}
  -- Red Hat Certified Instructor (RHCI) -- Red Hat Certified Examiner
  (RHCX) -- IBM Certified Linux Instructor.

  \paragraph{Languages}\label{languages}

  Perl -- Python -- TCL -- Bash -- English -- Spanish.

  \paragraph{Presentations, Projects, and
    Community}\label{presentations-projects-and-community}

  Prepared and given numerous
  \href{http://presentation.goozbach.com/}{presentations} at conferences
  and special interest groups.

  I am active in my local Linux users groups,
  \href{http://ale.org/}{Atlanta Linux Enthusiasts} and
  \href{http://chugalug.uga.edu/}{Classic Hackers UGA Linux Users Group}.

  I am the Author of/Contributor to these
  \href{http://github.com/goozbach/}{open source projects}.

\end{document}
